The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-21 ms.Rmd
fixing weird greying issue with response curve

# load both images
r_map <- brick('figs/interactive_map.png')
r_resp <- brick('figs/fengChangeWorkflow-2.png')

@@

# plot the response curve
plotRGB(r_resp, maxpixels = Inf)

>>>>

# load both images
r_map <- brick('figs/interactive_map.png')
r_resp <- raster('figs/fengChangeWorkflow-2.png')
r_resp <- brick(r_resp, r_resp, r_resp)

@@

# plot the response curve
plotRGB(r_resp, maxpixels = Inf,
        scale = max(maxValue(r_resp)))
